
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[main=english,czech]{babel}

\begin{document}

\section{setting}

The game takes place in a fictional us national park.
It is in the desert as the giftee likes national parks in the desert.

\subsection{visual design}

The ground is flat. There are cactuses. There is a geyser.

\subsection{effects on gameplay}

Cactuses are used for everything.

\section{plot}

There was a giant storage of oil found in the ground under the park and
there is a big company interested in harvesting it. There is a radio tower
able to send a distress signal, but you have no energy to power it.
Thankfully there is a generator that can be fed by cacti. You need
to keep it powered for enough time to charge an accumulator, which can then
use all it's power at once to send the distress signal.

\section{gameplay}

You can play as one of multiple classes. All of them can plant and water cacti
and shoot some kind of gun.

\subsection{classes}

\subsubsection{normal}

A class all others classes \textit{inherit} from.
It has a cactus powered smg. Reloading it damages a cactus, but can't destroy it.
It can water cacti with right click.

\subsubsection{heavy}

It's gun is different. The gun depletes the whole cactus (the cactus has to be
large). It shoots a giant projectile with a big knockback. The heavy can also
push normal units and block the buldozer.

\subsubsection{gardener}

Doesn't have a cactus powered gun or a water thing. It has a water gun.
The gun has two shoot modes: stream and a water ball. Both water cacti.
Water stream can only damage drones. Water ball has knockback and a slight
damage.

\subsection{enemy units}

They try to get to the radio tower and destroy it.

\subsubsection{drones}

They can fly ower your cacti, but are very weak.

\subsubsection{normal}

They damage cacti a bit, but get killed.

\subsubsection{buldozer}

Goes through cacti you build very easily. Slow and a bit tanky. Basically
a boss.

\subsection{cacti types}

\begin{itemize}
	\item small - enemies take small damage, but walk over it
	\item medium - normal enemies take damage and destroy it
	\item big - normal enemies take damage, but die and the cactus is transformed to medium
\end{itemize}

Watering a cactus makes it grow.

\end{document}
